\cvsection{Professional Experience}

\begin{cventries}

  \cventry
    {Principal Engineer}
    {\cvcompany{\href{https://humain.com/}{Humain}}{Riyadh}}
    {May 2026 -- Present}
    {
      \begin{cvitems}
        \item {Led the development and implementation of the \textbf{Humain One Platform SDK} monorepo, delivering the \textbf{h1} CLI, generated SDK libraries, adapter gateway, documentation pipeline, verification gates, and agent-skill workflows end to end.}
        \item {Built the SDK authority model that turns upstream service contracts into governed TypeSpec/OpenAPI outputs, generated clients, route manifests, Postman collections, proof artifacts, and developer-facing documentation.}
        \item {Created the foundation for agent-driven Humain One development, where Jira tickets and PRDs can be executed through coding-agent skills, the \textbf{h1} CLI, SDK libraries, and the in-house \textbf{Design System Library}.}
        \item {Replaced manual service integration patterns with deterministic, repo-verified delivery workflows that help human engineers and coding agents build new Humain One modules with consistent architecture, UI, SDK usage, and quality gates.}
      \end{cvitems}
    }

  \cventry
    {Lead Software Engineer}
    {\cvcompany{\href{https://humain.com/}{SCAI / Humain}}{Riyadh}}
    {Apr 2025 -- Apr 2026}
    {
      \begin{cvitems}
        \item {Led the development of the \textbf{Agentic AI Data Capturing Service} within the Humain One Platform, a large-scale AI-first ERP system spanning multiple engineering streams.}
        \item {Designed and implemented agentic AI workflows, building autonomous agents that orchestrate complex multi-step enterprise tasks.}
        \item {Previously led development of a \textbf{Smart Surveillance System} using computer vision for real-time threat detection and automated alerting.}
        \item {Architected a \textbf{Smart Traffic Management System} with border control integration, leveraging ML models for vehicle classification and license plate recognition.}
        \item {Drove full-stack delivery across frontend (React/Next.js), backend (Python, Spring Boot), ML pipelines, and edge deployment for low-latency IoT inference.}
        \item {Mentored engineers and established best practices for code quality, CI/CD, and agile delivery across concurrent AI products.}
      \end{cvitems}
    }

  \cventry
    {Engineering Consultant, Software Engineering}
    {\cvcompany{\href{https://site.sa/}{Saudi Information Technology Company (SITE)}}{Riyadh}}
    {Jan 2023 -- Mar 2025}
    {
      \begin{cvitems}
        \item {Led multiple platforms within the \textbf{Haseen Portal}, the National Cybersecurity Portal, ensuring secure and scalable delivery.}
        \item {Designed a company-wide \textbf{design system library}, standardizing UI components across engineering teams.}
        \item {Built and deployed an \textbf{internal AI assistant} serving 50+ engineers for code generation and knowledge management.}
        \item {Refactored legacy codebases, improving application performance by 30\% and reducing technical debt.}
        \item {Managed sprint planning and delivery across multiple projects using Azure DevOps.}
        \item {Mentored junior developers and led technical training sessions.}
      \end{cvitems}
    }

  \cventry
    {Software Engineer}
    {\cvcompany{\href{https://site.sa/}{Saudi Information Technology Company (SITE)}}{Riyadh}}
    {Feb 2020 -- Dec 2022}
    {
      \begin{cvitems}
        \item {Developed and maintained platforms within the Haseen Portal, the National Cybersecurity Portal.}
        \item {Built secure full-stack web applications with robust testing and deployment protocols.}
        \item {Introduced security measures and testing protocols, enhancing application resilience and release efficiency.}
      \end{cvitems}
    }

\end{cventries}
